Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
expertise paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson \& Weinstein, 2006; Kounin, 2006). Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom. This ability is referred to as classroom professional vision (Goodwin, 1994; Sherin, 2007). The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations (``knowledge-based reasoning''; Seidel \& Stürmer, 2014). Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions. According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold \& Holodynski, 2017). Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017). Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (Grub et al., 2020, p.75). Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner et al., 2016; Wolff et al., 2016).

\hypertarget{theoretical-background}{%
\section{Theoretical background}\label{theoretical-background}}

\hypertarget{professional-competence-in-teaching-profession}{%
\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}}

Competence is a common term in everyday school life. In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective. In the same way, the term competence can be applied to teachers. Teachers have to be competent in things such as teaching, educating, evaluating or innovating. Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig \& Rauch, 2008). They replace the rigid canon of knowledge that defined professional qualification for generations. In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.). To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf.~Klieme et al., 2008, p.~4). In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.

@@

The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' (cf.~Epstein \& Hundert, 2002; cited in Kunter et al.~2013, p.~807). Several studies could prove that this idea can be successfully transferred to the teaching profession (cf.~Goodmann et al., 2008; Oster, Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807). Accordingly, a quality standard can be applied to assess the quality of a teacher. This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano \& Pickering, 2003). Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher. Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003). This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.

\hypertarget{classroom-management}{%
\subsection{Classroom Management}\label{classroom-management}}

@@

However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle. This trained handling, as described above, can be summarized under the aspect of professional competence. It is expressed, among other things, in knowledge about classroom management (Grub, Biermann \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.

Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, van den Bogert, Jarodzka \& Boshuizen, 2015). Marzano et al.'s (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching. In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015). Therefore, it is often referred to as the central variable of successful teaching (Helmke \& Helmke, 2015). Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015). While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.

@@

Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf.~Wolff et al., 2015, p.~71). These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.). If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction. This is crucial to maximize students' active learning time (Helmke \& Helmke, 2015). It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research. In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).

\hypertarget{interdependence-of-classroom-management}{%
\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}}

In research, various models exist for approaching the concept of classroom management. However, they are very similar in their core statements. Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms. In the following, the network of effects of classroom management according to Helmke (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.

As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom. Helmke (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time. This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219). Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.

The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are ``interrelated with the quality of teaching and personal relationships'' (Helmke \& Helmke, 2015, p.5). It should not be forgotten that this space never functions in isolation and independently of other influences. It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015). But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke, 2014).

Classroom management itself is made up of various components which, according to Helmke (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior. Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).

The importance of rules in the classroom has been known and researched for some time. Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules (cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements \& Martin, 1982; cited in Doyle, 1989, p.~15). Although he also stresses that establishing a system of rules is a difficult task. Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989). Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).

As a result, students significantly influence these rules by their willingness to follow them. Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke \& Helmke, 2015). This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done. needs to be done. In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke, 2014). For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.

No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.~122); the effect size is \emph{d} = 1.42. (Helmke \& Helmke, 2015, p.~6). The behavioral pattern of presence is not a new concept. It was already recorded by Kounin in 1970 under the term \emph{withitness}. Later research confirmed and validated his assumptions and definition of the term (cf.~Helmke, 2014, p.10). In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times. This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015). Presence can consequently be illustrated very vividly by means of the image of ``eyes in the back of the head'' (Kounin, 2006). In addition to presence, Kounin (2006) uses the term overlap. It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom. The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017). When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020.). Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness.
and increases general awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.

As a third component influencing the quality of classroom management, cites Helmke (2014) time use and management. This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway. However, Helmke \& Helmke (2015, p.~6) emphasize how elementary it is to identify and minimize possible ``time thieves''. This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.). If these take up too much space in the classroom, less time is available for teaching important lesson content. This can be prevented by teachers minimizing such ``time thieves'' in advance through well-planned classroom management.

@@

\hypertarget{professional-vision}{%
\subsection{Professional vision}\label{professional-vision}}

Competence assessment plays a central role in the teaching profession and its training. It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004). In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (Barth, 2017). Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel \& Prenzel 2014). The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001). It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations. Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences. In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.~Sherin, 2001, p.~75). What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments. Goodwin (1994, p.606) defines professional vision as ``socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group'' (cited in Sherin, 2001, p.~75). It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001). Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive. In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.~Sherin, 2001, p.75). This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.

\hypertarget{teachers-professional-vision}{%
\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

@@

\linenumbers
\usepackage{csquotes}
\usepackage[titles]{tocloft}
\cftpagenumbersoff{table}
\renewcommand{\cfttabpresnum}{\itshape\tablename\enspace}
\renewcommand{\cfttabaftersnum}{.\space}
\setlength{\cfttabindent}{0pt}
\setlength{\cftafterloftitleskip}{0pt}
\settowidth{\cfttabnumwidth}{Table 10.\qquad}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions},
  pdfauthor={Mandy Klatt1, Dr.~Gregor Kachel1, 2, Dr.~Christin Lotz1, \& Prof.~Dr.~Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={professional vision, expertise, classroom management, mobile eye-tracking},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\section{Introduction}\label{introduction}

Managing classroom disruptions is a crucial aspect of effective classroom management (Evertson, Weinstein, et al., 2006; Kounin, 2006). Accordingly, teachers must be able to quickly notice and appropriately react to significant events in the classroom. This ability is referred to as classroom professional vision (\textbf{goodwin2015?} professional; Sherin, 2007). The process of professional vision can be divided into two main aspects: focusing on relevant situations for learning and teaching (``noticing'') and applying knowledge to draw appropriate conclusions in these situations {[}``knowledge-based reasoning''; Seidel and Stürmer (2014){]}. Therefore, the early visual perception of classroom disruptions is a key component to effectively maximize students' learning time and minimize classroom interruptions. According to Kounin (2006), these important classroom management strategies are called ``withitness'' and ``overlapping'' and can be summarized under the concept of monitoring (Gold \& Holodynski, 2017). Learning to develop such classroom management skills is a demanding and complex task for student teachers (Wolff et al., 2017). Research on teacher expertise showed that expert and novice teachers differ in their ability to perceive classroom events, ``{[}\ldots{]} whereas only a few studies have focused on the basal process of noticing, i.e.~the recognition of possible disturbing situations'' (\textbf{grub2020processp?}). Mobile eye-tracking data can fill this research gap by providing new insights in how expertise differences in teacher´s professional vision manifest in teacher-student interactions (Lachner, Jarodzka, \& Nückles, 2016; Wolff, Jarodzka, Bogert, \& Boshuizen, 2016).

\section{Theoretical background}\label{theoretical-background}

\subsection{Professional competence in teaching profession}\label{professional-competence-in-teaching-profession}

Competence is a common term in everyday school life. In most cases, it refers to the acquisition of competencies by students and how to promote them and make them effective. In the same way, the term competence can be applied to teachers. Teachers have to be competent in things such as teaching, educating, evaluating or innovating. Therefore, competencies form an important and practical contribution in current educational research and teacher education (Klieme, Hartig, \& Rauch, 2008). They replace the rigid canon of knowledge that defined professional qualification for generations. In recent years, the concept of competence has experienced an upswing and is in the focus of educational research in particular (ibid.). To put it simply, the concept of competence in empirical research deals with the development of human resources and the productivity of education (cf. Klieme et al., 2008, p. 4). In order to be able to make a meaningful conceptualization definition of competence, it is necessary to take a closer look at different of research have to be considered in more detail.

@@

The term ``professional competence'' is the application of the concept to working life, particularly in highly complex and demanding professions, in which mastery of situations is especially dependent on the interplay of knowledge, skills, attitudes, and motivation.'' {[}cf. Epstein and Hundert (2002); cited in Kunter et al.~2013, p.~807{]}. Several studies could prove that this idea can be successfully transferred to the teaching profession {[}cf.~Goodmann et al., 2008; Oser, Achtenhagen, and Renold (2006), Achtenhagen \& Renold, 2006; Tannenbaum \& Rosenfeld, 1994; cited in Kunter et al., 2013, p.~807{]}. Accordingly, a quality standard can be applied to assess the quality of a teacher. This quality is elementary in the school context because the teacher factor most influences student learning (Marzano, Marzano, \& Pickering, 2003). Thus, the effectiveness of education and the learning growth of individual students can be enhanced by the teacher. Research has shown that this component can even offset the influence of an ineffective school setting (Marzano et al., 2003). This effect places teachers at the center of ensuring effective teaching and learning and underscores the importance of professional competence in this career field.

\subsection{Classroom Management}\label{classroom-management}

@@

However, lessons, and specifically classroom disruptions, are unpredictable as well as multifaceted and require a high level of expertise and competence on the part of the teacher to handle. This trained handling, as described above, can be summarized under the aspect of professional competence. It is expressed, among other things, in knowledge about classroom management (Grub, Biermann, \& Brünken, 2020) and can be understood as a manifold toolbox of teachers to find their way in the challenging environment of the classroom.

Classroom management significantly influences the ability to perceive and subsequently respond to classroom events and thus organize for disruption-free instruction (Wolff, Bogert, Jarodzka, \& Boshuizen, 2015). Marzano et al. (2003) research created a foundational work in school and developmental research by manifesting that instructional strategy, curriculum design, and classroom management are significant roles in effective teaching. In this regard, research agrees that effective leadership and effective learning are closely related and classroom management can be considered a key component of teaching (Wolff et al., 2015). Therefore, it is often referred to as the central variable of successful teaching (Helmke \& Helmke, 2015). Good classroom management is thus the prerequisite for learning to take place (Wolff et al., 2015). While the term suggests that it is mainly about rituals, rules, or measures that are meant to maintain order within the classroom, it is about much more than these two components.

@@

Ultimately, classroom management is composed of a set of multifaceted skills that include classroom structure and atmosphere, instructional decisions made by the teacher, and pedagogical as well as practical knowledge (cf. Wolff et al., 2015, p. 71). These skills essentially determine teacher decisions, interactions, and exchanges in the course of instruction (ibid.). If these very skills are well-developed, they guarantee a smooth and trouble-free course of instruction. This is crucial to maximize students' active learning time (Helmke \& Helmke, 2015). It, in turn, has been shown to correlate positively with achievement growth and learning interest in a class (Helmke, 2008), placing effective classroom management at the center of empirical research. In principle, these skills can be developed in the course of teaching education, as well as subsequent professional experience, which is why they constitute an essential component of teacher expertise (Wolff et al., 2015).

\subsubsection{Interdependence of classroom management}\label{interdependence-of-classroom-management}

In research, various models exist for approaching the concept of classroom management. However, they are very similar in their core statements. Therefore, it is merely a matter of preference which concept is consulted to explain connections and terms. In the following, the network of effects of classroom management according to Helmke et al. (2014) is used as a reference model in order to be able to understand the embedding of the concept accordingly.

As was made clear in the definition, classroom management is a complex construct that attempts to accommodate the various modes and challenging characteristics of a classroom. Helmke et al. (2014) therefore depicts classroom management as a complex web of effects (see Figure 2) that serves the overarching goal of maximizing active learning time. This has a particularly high value in school and development research and is considered a predictor of learning success, which could be confirmed in a meta-study (\emph{d} = 0.39; Hattie, 2013, p.219). Due to this diversity of aspects to be investigated, classroom management is a fundamental research topic.

The concepts, strategies and techniques used to implement successful classroom management depend first and foremost on various teacher characteristics and are ``interrelated with the quality of teaching and personal relationships'' (Helmke \& Helmke, 2015, p.5). It should not be forgotten that this space never functions in isolation and independently of other influences. It is embedded in diverse contexts, especially in the school and class context (Helmke \& Helmke, 2015). But also the cooperation with parents, a healthy evaluation culture, as well as the professional and didactic context have a significant impact on how effectively a class can be led (Helmke et al., 2014).

Classroom management itself is made up of various components which, according to Helmke et al. (2014), can be divided into four categories: Rules and Procedures, presence, Time Management, and Establishing Desirable and Reducing Undesirable Student Behavior. Rules are considered the non-plus ultra of proactive management in the classroom, to whose agreements students and teachers alike must adhere (Helmke \& Helmke, 2015).

The importance of rules in the classroom has been known and researched for some time. Doyle (1989) relied as early as the late 1980s on studies showing that effective classroom management is due to timely implemented rules {[}cf.~Emmer, Evertson \& Anderson, 1980; Emmer, Sanford, Clements, and Martin (1982); cited in Doyle, 1989, p.~15{]}. Although he also stresses that establishing a system of rules is a difficult task. Classroom rules are situation-dependent, as certain agreements only apply to certain phases of the lesson (for example, speaking quietly during group work; Doyle, 1989). Furthermore, order is always established jointly, in cooperation with the learners (Doyle, 1989).

As a result, students significantly influence these rules by their willingness to follow them. Procedures are another tool to maintain the flow of the lesson, as recurring routines provide learners with security and clarity (Helmke \& Helmke, 2015). This inevitably reduces the teacher's workload, eliminates additional explanations are no longer necessary, and it is clear to the learners at all times what needs to be done. needs to be done. In addition, teachers can present instructions for corresponding routines through non-verbal actions to save time (Helmke et al., 2014). For the reasons just reasons just explained, it is clear why Hattie (2013, p.~122) gives this component of classroom classroom management an effect size of \emph{d} = 0.76.

No other aspect of classroom management is as effective for classroom interruptions as the teacher's omnipresence (Hattie, 2013, p.~122); the effect size is \emph{d} = 1.42. (Helmke \& Helmke, 2015, p.~6). The behavioral pattern of presence is not a new concept. It was already recorded by kounin1970discipline under the term \emph{withitness}. Later research confirmed and validated his assumptions and definition of the term (cf. Helmke et al., 2014, p. 10). In order to be present, the teacher must be able to control the classroom adequately and superficially effectively at all times. This means she must be able to recognize relevant cues or situations that require possible action (Wolff et al., 2015). Presence can consequently be illustrated very vividly by means of the image of ``eyes in the back of the head'' (Kounin, 2006). In addition to presence, Kounin (2006) uses the term overlap. It is a kind of multitasking ability to be able to cope with parallel processes and situations in the classroom. The two dimensions of overlap and presence can also be summarized together under the term monitoring (Gold \& Holodynski, 2017). When talking about ongoing monitoring in the classroom, this process includes teachers' awareness of concurrent events as well as their demonstration of this to learners (Grub et al., 2020). Well-developed monitoring behaviors enable teachers to detect disruptions early and increase overall awareness of relevant events in the classroom (ibid.). From this point of view, it becomes clear why awareness is a core component of teacher competence.

As a third component influencing the quality of classroom management, cites Helmke et al. (2014) time use and management. This seems trivial at first, considering that classroom management serves the goal of maximizing learning time anyway. However, Helmke \& Helmke (2015, p.~6) emphasize how elementary it is to identify and minimize possible ``time thieves''. This includes factors such as unpunctuality or slow transitions, as well as the underemployment of learners (ibid.). If these take up too much space in the classroom, less time is available for teaching important lesson content. This can be prevented by teachers minimizing such ``time thieves'' in advance through well-planned classroom management.

@@

\subsection{Professional vision}\label{professional-vision}

Competence assessment plays a central role in the teaching profession and its training. It follows the approach of concentrating on action-relevant as well as lesson-related content in order to train corresponding competences for teaching practice (KMK, 2004). In order for teachers in heterogeneous classrooms to be able to filter relevant teaching aspects, they need knowledge about the control of their attention processes (V. L. Barth, 2017). Science summarizes this competence under the so-called professional vision, which is now a widely empirically studied research topic (Jahn, Stürmer, Seidel, \& Prenzel, 2014). The concept of professional vision can originally be traced back to the anthropologist Charles Goodwin and became known under the term Professional Vision (Sherin, 2001). It provided the answer to Goodwin's question regarding the development of a professional vision, in the context of the profession, compared to the vision of everyday situations. Goodwin uses the comparison of an archaeologist and a layperson to figuratively describe the differences. In doing so, he investigated which ability it is that makes the archaeologist see and interpret a landscape differently than the layperson (cf.~Sherin, 2001, p.~75). What looks to the former merely like sand, rocks and stones, is to the trained eye of the archaeologist a base of a column or architectural fragments. Goodwin (1994, p.606) defines professional vision as ``socially organized ways of seeing and understanding events that are answerable to the distinctive interests of a particular social group'' (cited in Sherin, 2001, p.~75). It is assumed that one can see certain phenomena or occurring events in a certain way due to one's professional affiliation (Sherin, 2001). Particularities are more easily recognized because the gaze becomes more trained over time and thus profession-relevant features appear more distinctive. In the previous example of the archaeologist, this would mean that he noticed variations in color, texture and sand and saw a cluster of stones as a possible element of a larger structure (cf.~Sherin, 2001, p.75). This distinguishes experts significantly in their visions from non-experts in the field, as they had learned to filter their environment for crucial features.

\subsubsection{Teachers' professional vision}\label{teachers-professional-vision}
